Automated Theorem Proving Based on the Calculus of Positively Constructed Formulas\thanks{Ok}

### 2015-08-24 paper.tex
Title slightly corrected.

% first the title is needed
\title{Automated Theorem Proving Based on the Calculus of Positively Constructed Formulas}
% a short form should be given in case it is too long for the running head
\titlerunning{ATP Based on the PCF Calculus}

% the name(s) of the author(s) follow(s) next
%
% NB: Chinese authors should write their first names(s) in front of
% their surnames. This ensures that the names appear correctly in
% the running heads and the author index.
%
\author{Alexander Larionov%
\thanks{Ok}%
\and Artem Davydov\and Evgeny Cherkashin\and Ivan Terekhin}
%
%\authorrunning{Lecture Notes in Computer Science: Authors' Instructions}
% (feature abused for this document to repeat the title also on left hand pages)

% the affiliations are given next; don't give your e-mail address
% unless you accept that it will be published
\institute{Irkutsk State University,
              1, Karl Marks str., Irkutsk, Russia \\
           Institute for System Dynamics and Control Theory,
              134, Lermontov str., Irkutsk, Russia   
%\mailsa\\
%\mailsb\\
%\mailsc\\
%\url{http://www.springer.com/lncs}
}

@@

>>>>

% first the title is needed
\title{Automated Theorem Proving Based on the Calculus of Positively Constructed Formulas\thanks{Ok}}
% a short form should be given in case it is too long for the running head
\titlerunning{ATP Based on the PCF Calculus}

% the name(s) of the author(s) follow(s) next
%
% NB: Chinese authors should write their first names(s) in front of
% their surnames. This ensures that the names appear correctly in
% the running heads and the author index.
%
\author{Alexander Larionov\and Artem Davydov\and Evgeny Cherkashin}
%
%\authorrunning{Lecture Notes in Computer Science: Authors' Instructions}
% (feature abused for this document to repeat the title also on left hand pages)

% the affiliations are given next; don't give your e-mail address
% unless you accept that it will be published
\institute{Irkutsk State University,
              1, Karl Marks str., Irkutsk, Russia \\
           Institute for System Dynamics and Control Theory at Siberian Branch
              of Russian Academy of Sciences,
              134, Lermontov str., Irkutsk, Russia\\
           Irkutsk National Research Technical University,
              83, Lermontov str., Irkutsk, Russia
%\mailsa\\
%\mailsb\\
%\mailsc\\
%\url{http://www.springer.com/lncs}
}

@@

%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:
